---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# shelve: Simple interface to store objects on disk for later use

<!-- badges -->
[![R](https://img.shields.io/badge/language-R-blue)]()
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange)]()
<!-- badges -->

## Installation 

```r
pak::pkg_install("markheckmann/shelve")
```

## Idea

The `shelve` package tries to better integrate report generation into your R code.
When creating a report, a common way ist to use Rmarkdown/Quarto. This is useful for many instance. However, I find that using it that this somewhat restrict for my way of working.

There are a few relevant concepts: 

- `shelf`: A storage for objects
- `shelve`, `unshelve`: Add and retrieve something from a shelf


```{r eval=TRUE}
library(shelve)

shelf_list()
shelf_active()
shelf_activate("test")
shelf_list()
shelf_remove("test")

shelf_clear()
shelf_files()
shelve(mtcars, "cars")
shelf_files()

unshelve("cars") |> head()
```

Create a report from a shelf.


## Storing objects locally

There are different options to store data on disk. To preserve data between sessions, we use the `hoards` package, which use `rappdirs` under the hood. 
