---
title: "Idea"
output: html_document
date: "2024-01-27"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Misc


## Idea

The `shelve` package tries to better integrate report generation into your R code.
When creating a report, a common way ist to use Rmarkdown/Quarto. This is useful for many instance. However, I find that using it that this somewhat restrig for my way of working.

There are to types of concept: 

- `shelf`: A storage for objects
- `shelve`: Putting something into a shelf
- `unshelve`: Retrieve something from a shelf

The package functions usually start with one of the two word.

```{r eval=TRUE}
library(shelve)

shelf_list()
shelf_active()
shelf_activate("test")
shelf_list()
shelf_remove("test")

shelf_clear()
shelf_files()
shelve(mtcars, "cars")
shelf_files()

unshelve("cars") |> head()
```

Create a report from a shelf.


## Storing objects locally

There are different options to store data on disk. To preserve data between sessions, we use the `hoards` package, which use `rappdirs` under the hood. 
